\documentclass{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{lipsum}

\name{Nikola Samardzic}

\begin{document}
\makeheader

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROJECTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{ResumeSection}{Publications}
    \begin{ResumeSubsection}{
            org={F1: A Fast and Programmable Accelerator for Fully Homomorphic Encryption},
    position={\textbf{N. Samardzic$^*$}, A. Feldmann$^*$, et al. (MICRO'21)}}
        \begin{itemize}
            \item F1 is a hardware accelerator (ASIC) for computation on encrypted data.
            \item F1 accelerates machine learning benchmarks by 1,000-10,000$\times$
            \item Pushes time for a private DNN inference from 20 minutes to 250 
                \emph{milliseconds}; first to show that real-time private DNN 
                inference in the cloud is possible.
        \end{itemize}
    \end{ResumeSubsection}


    \begin{ResumeSubsection}{org={Bonsai: High-Performance Adaptive Merge Tree Sorting},
    position={\textbf{N. Samardzic$^*$}, W. Qiao$^*$, et al. (ISCA'20)}}
        \begin{itemize}
        \item The fastest sorter for the 4-64$\,$GB range.
            FPGA implementation based on the merge sort algorithm.\vspace{0.3cm}
        \end{itemize}
        \footnotemark[1]{\textbf{Authors contributed equally}}
\end{ResumeSection}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{ResumeSection}{experience}
    \begin{ResumeSubsection}{org={NAND Capital},
        position={Software Engineering Intern},
        duration={2020/01 - 2020/04}}
        \begin{itemize}
            \item NAND is an options trading hedge fund.
                I was the first employee (intern) working with the two founders. 
            \item Diagnosed and fixed 
                issues related to Monte Carlo simulation of fat-tailed distributions; 
                backtesting revealed that these 
                techniques removed the majority of orders placed by the system that generated
                losses of over 10\%.
            \item Developed a backpropagation algorithm for the main prediction pipeline 
                that guarantees 
                improvement in backtested rate of return after each training batch. 
            \item Interviewed candidates and participated in hiring decisions. Recommended
                two UCLA friends that eventually came to work for NAND.
        \end{itemize}
    \end{ResumeSubsection}
        \begin{ResumeSubsection}{org={Goldman Sachs},
            position={Research Intern},
            duration={2019/06 - 2019/09}}
            \begin{itemize}
            \item Automated an accounting task previously performed 
                full-time by two people; used latest Natural Language 
                Processing (NLP) techniques. 
            \item Ported training and inference infrastructure to AWS GPUs, improving
                training time by 10$\times$.
            \end{itemize}

    \end{ResumeSubsection}
    \begin{ResumeSubsection}{org={SpaceX},
        position={Software Engineering Intern},
        duration={2017/06 - 2017/09}}
        \begin{itemize}
            \item Was offered full-time software engineering job as a Freshman 
                in college. 
            \item Tools I developed save 7.5 weeks of engineering time per rocket.
            \item Created software to automate defining and testing of all
                propulsion joints on SpaceX rockets. Created tool for automatically
                generating repair and inspection plans for propulsion joints. 
        \end{itemize}

\end{ResumeSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{ResumeSection}{education}
    \begin{ResumeSubsection}{org={Massachusetts Institute of Technology (MIT)},
        position={Ph.D. in Electtrical Engineering and Computer Science (EECS)},
        duration={2020/08 - Present}}
        \begin{itemize}
            \item Advisor: Prof. Daniel Sanchez; Area: Computer Architecture; GPA: 4.00 / 4.00
            \item Coursework: Computer Networking, Computer Architecture, and Machine Learning
            \item My research was funded by DARPA, NSF, Wistrom, Samsung, and the MIT Graduate Fellowship.
        \end{itemize}
    \end{ResumeSubsection}
    
    \begin{ResumeSubsection}{org={University of California, Los Angeles (UCLA)},
        position={B.Sc. in Computer Science},
        duration={2016/09 - 2020/06}}
        \begin{itemize}
            \item GPA: 3.98 / 4.00; Summa Cum Laude and Phi Beta Kappa
            \item Additional math coursework: Linear Algebra Honors, Ring Theory Honors,
                Galois Theory, p-Adic Numbers, Analysis II Honors.
        \end{itemize}
    \end{ResumeSubsection}
\end{ResumeSection}


\end{document}

